---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```


Page 1 {data-orientation=rows}
===================================== 

Row
-----------------------------------------------------------------------

### This dashboard is updating trend from Bay Wheels in latest data (October 2022). Trip volume are pretty equally distributed in October.

```{r fig.height = 4, fig.width = 17}
library(tidyverse)
library(ggmap)
library(skimr)
library(lubridate)
library(forcats)
library(patchwork)
ggmap::register_google(key = "AIzaSyCGPPRgTcFbQUi4LNVc-TVZaaE17jzDa5M")
df <- read_csv("data/202210-baywheels-tripdata.csv")
t <- ymd_hms(df$started_at )
df_time <- tibble(
  date = date(t),
  month = month(t, label = T),
  wday = wday(t, label = T),
  mday = mday(t),
  hours = hour(t)
)
df3 <- df_time %>% 
  group_by(hours)%>%
  summarize( count = n())
df4 <- df_time %>% 
  group_by(wday)%>%
  summarize( count = n())

p1 <- ggplot(df3, aes(x = hours, y = count)) + 
  geom_col(alpha = 0.6, fill="#69b3a2")+ 
  ggtitle("Trips Volume by Hours") + ylab(" ") + xlab(" ")+
  theme(plot.title = element_text(size = 10))
p2 <- ggplot(df4, aes(x = wday, y = count)) + 
  geom_col(alpha = 0.6, fill="#69b3a2")+ 
  ggtitle("Trips Volume by Week Days") + ylab(" ") + xlab(" ")+
  theme(plot.title = element_text(size = 10))


t1 <- ymd(df$started_at )
df5 <- tibble(
  date = date(t))  %>%
  group_by(date)%>%
  summarize( count = n())

lbls <- paste0(month.abb[month(df5$date)], " ", lubridate::mday(df5$date) )
brks <- df5$date 

p <- ggplot(df5, aes(x=date, y=count)) +geom_line(color="#69b3a2")  + 
  geom_point(color = "#69b3a2") +
  scale_x_date(labels = lbls,breaks = brks) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust=1, size = 6), 
        axis.text.y = element_text(size = 6),
        plot.title = element_text(size = 10),
        panel.grid.minor = element_blank(),
        legend.position = "none") + ylab(" ") + xlab(" ")
p 
```

Row 
-----------------------------------------------------------------------

###  Volume seem to be equally among days in a week, this can be interpreted that people are get used to using the bike service daily.

```{r fig.height = 5, fig.width = 8}
p2
```

### There is high volume at around 5pm every day, which mean many people use Bay Wheels for commuting.

```{r fig.height = 5, fig.width = 8}
p1
```

Page 2 {data-orientation=columns}
===================================== 

Bikes are used mostly in San Francisco, Oakland, and San Jose.

    
Column
-------------------------------------
    
### Bay Area
    
```{r}
ggmap_center <- ggmap::get_googlemap(center = c(lon = -122.25, lat = 37.5), 
                                     zoom = 10,
                                     maptype = 'roadmap')
ggmap(ggmap_center) +
  geom_point(data = df, aes(x = start_lng, y =  start_lat), size = 0.5,  color="#1B4F72", alpha = 0.4,) 
```
   
Column
-------------------------------------
   
### San Jose

```{r }
ggmap_center <- ggmap::get_googlemap(center = c(lon = -121.9, lat = 37.31), 
                                     zoom = 11,
                                     maptype = 'roadmap')
ggmap(ggmap_center) +
  geom_point(data = df, aes(x = start_lng, y =  start_lat), size = 0.5,  color="#1B4F72", alpha = 0.6,) 
```   
 
### San Francisco
    
```{r }
ggmap_center <- ggmap::get_googlemap(center = c(lon = -122.44, lat = 37.76), 
                                     zoom =12,
                                     maptype = 'roadmap')
ggmap(ggmap_center) +
  geom_point(data = df, aes(x = start_lng, y =  start_lat), size = 0.2,  color="#1B4F72", alpha = 0.3,) 
```


